Instructions for TTO 2019 Proceedings

### 2021-07-05 article/test.tex
n-th update
cosmetic changes

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{tto2019}
\usepackage{times}
\usepackage{latexsym}
\usepackage{multicol}
\usepackage{graphicx}

\usepackage{url}

@@

In this article, we focus on MSMP's policies and actions regarding content with low credibility or false information, commonly referred to as {\it Fake News}.\footnote{For an overview on the {\it concept} of {\it Fake News}, we refer the reader to the article The science of fake news by Lazer et al. (2018)~\cite{lazer}.} The {\it Fake News} phenomenon is still ill-defined by the academic community as it encompasses several combined features such as spreading inaccurate, false or misleading information, with or without the intention of influencing or manipulating a target pool of audience. The rise of social networking platforms over the last decade in terms of number of users worldwide and volume of content, has modified the information ecosystem in terms of production of information and its mediation. Many users can now produce and share content which includes news related information, without having to abide by strict editorial processes that ensure accuracy of information and reliability of sources. In particular, false or inaccurate content produced and shared on social networking platforms concerning the political life or public health may have a potentially harmful impact on the society, in the rare event that it goes viral. This gave rise to a set of heterogenous fact-checking policies across mainstream platforms.

@@

\bigskip

%{\color{red} Policies not specific to misinformation, but to enforce laws + things already used for terrorism and hate speech. Intro or/and Discussion. accounts: hard to say suspension for which.}

%Content can be withheld in compliance to specific laws of each country, ex: ..;
% Misinformation : which law ? not defined !

\begin{table}[]
\centering
\begin{tabular}{|l|l|l|l}

\hline
&  \begin{tabular}[c]{@{}l@{}} Application Programming Interface (API)  \end{tabular}                                                                                                                                                                                                                                                                                                                                                                                                                                            &    \multicolumn{1}{l|}{Web Scraping}                                                                                                                                                                   \\ \hline
Facebook & \begin{tabular}[c]{@{}l@{}}\href{https://www.crowdtangle.com}{CrowdTangle}: public content insights tool \\ owned and operated by Facebook. \\ \href{https://buzzsumo.com}{Buzzsumo}: commercial content database  \end{tabular}                                                                                                                                                                                                               &      \multicolumn{1}{l|}{}    
\\ \hline
Twitter  &  \href{https://developer.twitter.com/en/docs/twitter-api/early-access}{Twitter API V2} & \multicolumn{1}{l|}{\href{https://github.com/medialab/minet/blob/master/docs/cli.md\#twitter-scrape}{Minet twitter scrape}}                                                                                                                                                                           \\ \hline
Youtube  &  \href{https://developers.google.com/youtube/v3}{Youtube API V3}      &                                                                                                                            \multicolumn{1}{l|}{}                                                                                                                                                                           \\ \hline
\end{tabular}
\caption{Data collection}
\label{tab1}
\end{table}

 %We We are aware that other APIs or databases can be useful on that matter, but we will only mention here the ones about which we have some experience.

%CrowdTangle is a public insights tool owned and operated by Facebook, that exclusively tracks public content from Facebook public groups and pages. BuzzSumo is a commercial content database that tracks the volume of user interactions with internet content on Facebook, Twitter, and other social media platforms.

%Section 230 in the US + EU 
%Pressure to moderate and mix-up of platforms with public square… 
%Rôle dans la production/médiation : P-M-R 
%Pourquoi faut-il vérifier leurs politiques ? D’une part parce que ce sont les plateformes elles-mêmes qui annoncent leurs effets. D’autre part beaucoup de choses indirectes. 
%
%Add disclaimer in a footnote early on in the document : document not meant to be an exhaustive overview of all the existing regulations and point to three or four main legal sources for exhaustive references.

%Such policies include the introduction of notices (Twitter, see link) or flags (Facebook, see…) to signal to users inaccurate or false content, the temporary or permanent suspension of accounts (Twitter) or pages (Facebook), reducing the visibility of posts or pages (Facebook), or blocking users from sharing specific URL links (see link). The objective of this article is twofold. First, we study the impact of a number of  implemented measures by mainstream platforms to tackle (mis)disinformation.

@@

When an account is permanently suspended by Facebook, it disappears from the platform (so its data cannot be scrapped anymore), and its data also disappears from the CrowdTangle API.\footnote{CrowdTangle is a public insights tool owned and operated by Facebook, that exclusively tracks public content from Facebook public groups and pages.}

Interestingly, Facebook is regularly publishing a monthly {\it coordinated inauthentic behavior} report where it informs how many personal accounts, pages or groups were deleted and to which {\it deceptive network} they may have belonged.\footnote{See the April 2021 report for an example: \href{https://about.fb.com/news/2021/05/april-2021-coordinated-inauthentic-behavior-report/}{https://about.fb.com/news/2021/05/april-2021-coordinated-inauthentic-behavior-report/}} But as long as external persons do not have access to deleted accounts data, these reports cannot be verified by independent researchers or journalists.

@@

{\color{red} N.B. Manual decision, not the automatic strike system}
\begin{figure}
\centering
	\begin{multicols}{1}
		\includegraphics[scale=0.25]{./img/lifesite.jpg} 
	\end{multicols}
	\begin{multicols}{1}
		\includegraphics[scale=0.25]{./img/lifesite_rolling_7_lifesite.jpg}
	\end{multicols}
\caption{Panel (a): number of Tweets per day of the Twitter account $@Lifesite$ linked to the website lifesitenews.com from January, 2019 until April 2021. Panel (b): number of Tweets per day that have shared a lifesitenews.com URL link from January, 2019 until April 2021. }
\label{fig2}
\end{figure}

In this section, we discuss one case of temporary suspension on Twitter.\footnote{See the official documentation on the Twitter's Help Center regarding account suspension: \href{https://help.twitter.com/en/managing-your-account/suspended-twitter-accounts}{https://help.twitter.com/en/managing-your-account/suspended-twitter-accounts }.} The Twitter account of the website lifesitenews.com has been suspended for at least two periods of time: from end of 2019 until fall 2020 for 308 days, then again since January 2021 for having violated Twitter Rules\footnote{See Lifesitenews's article discussing the reason for the suspension: \href{https://www.lifesitenews.com/news/lifesite-is-dumping-twitter-and-so-should-you}{https://www.lifesitenews.com/news/lifesite-is-dumping-twitter-and-so-should-you}. Twitter rules can be found at: \href{https://help.twitter.com/en/rules-and-policies/twitter-rules}{https://help.twitter.com/en/rules-and-policies/twitter-rules}. }. In particular, this website has several failed fact-checks concerning the published articles, according to Iffy.news.\footnote{See \href{https://mediabiasfactcheck.com/life-site-news/}{https://mediabiasfactcheck.com/life-site-news/}}. We collected the activity (tweets, replies, quotes, retweets) on their Twitter account $@LifeSite$ via the Twitter API, using the historical search endpoint.\footnote{See the documentation: \href{https://developer.twitter.com/en/docs/twitter-api/tweets/search/api-reference/get-tweets-search-all}{https://developer.twitter.com/en/docs/twitter-api/tweets/search/api-reference/get-tweets-search-all}.} We then plotted the number of Tweets, Retweets, Quotes and Replies per day, as shown in panel $a$ of figure \ref{fig2}). The two periods of temporary suspension are clearly observed in the data as the user(s) of the account were not allowed to use the functionalities of the Twitter Platform.

@@

{\color{pink}The Beauty of life}

@@

One of Facebook’s measures to regulate misinformation is to reduce the spread of misleading content through ranking. Facebook ranks each post and ad with a relevancy score, a high score leading to a high likelihood of the post or the ad appearing in someone’s newsfeed. Facebook can thus make a post or a whole account less visible by decreasing the rank of its content.\footnote{Lyons, T. (2018, May 22). The three-part recipe for cleaning up your news feed. Facebook Newsroom. \href{https://about.fb.com/news/2018/05/inside-feed-reduce-remove-inform/}{about.fb.com/news/2018/05/inside-feed-reduce-remove-inform/}.} Such {\it reduce} action should be visible in the engagement metrics of the posts: if a post reaches less users because of a lower ranking, it is less likely to receive likes, comments and shares.

Owned by Alex Jones, Infowars is usually described as a misinformation website: it is on the Wikimedia global spam blacklist\footnote{See \href{https://meta.wikimedia.org/wiki/Spam\_blacklist}{meta.wikimedia.org/wiki/Spam\_blacklist}.}, was classified among websites that have posted deceptive content according to FactCheck.org\footnote{See \href{https://www.factcheck.org/2017/07/websites-post-fake-satirical-stories/}{https://www.factcheck.org/2017/07/websites-post-fake-satirical-stories/}.}, and its factual reporting has been rated {\it very low} by the Media Bias / Fact Check resource.\footnote{See the Iffy.news page: \href{https://mediabiasfactcheck.com/infowars-alex-jones/}{https://mediabiasfactcheck.com/infowars-alex-jones/}.} On May 2, 2019, Facebook announced they would prohibit users from sharing Infowars content unless they are explicitly condemning the material.\footnote{See \href{https://www.wired.com/story/facebook-bans-alex-jones-extremists/}{https://www.wired.com/story/facebook-bans-alex-jones-extremists/}.}

To verify the measure, we used the CrowdTangle API at the ‘/posts/search’ endpoint\footnote{see the documentation for more details: \href{https://github.com/CrowdTangle/API/wiki/Search}{github.com/CrowdTangle/API/wiki/Search}.} to collect the 37,242 Facebook public posts that shared a link containing ‘infowars.com’ and that were published between January 1, 2019 and December 31, 2020.\footnote{We found in the collected data some Facebook posts that did not directly share an Infowars link (but rather a YouTube or Facebook video containing an Infowars link in its description), thus we excluded such posts from our data to keep only the 27,721 posts directly sharing an Infowars link.} The command used can be found \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect_facebook_crowdtangle_infowars_data.sh}{here}.

The number of public posts sharing an Infowars link remained globally stable in 2019 (Figure \ref{infowars1} top panel), thus Facebook’s announced ‘ban’ did not appear to prevent users from sharing an Infowars link. Interestingly a clear drop in engagement was observed on May 2, 2019 (Figure \ref{infowars1} bottom panel). The number of reactions per post decreased by -94\% when we compared the two months before and after May 2, 2019, the shares decreased by -96\%, and the comments by -93\%.

@@

	\begin{multicols}{1}
		\includegraphics[scale=0.3]{./img/infowars/fb_infowars_1.png}
	\end{multicols}

	\begin{multicols}{1}
		\includegraphics[scale=0.3]{./img/infowars/fb_infowars_2.png} 
	\end{multicols}

	\caption{Public Facebook posts sharing an Infowars link in 2019 and 2020 gathered from the CrowdTangle API. The red line marks the date of May 2, 2019, when Facebook has announced the ban regarding Infowars. (Top panel) Number of daily posts. (Bottom panel) Engagement metrics (average number of reactions, shares and comments per post). }
	\label{infowars1}
\end{figure}

This would suggest that Facebook’s measure taken in May 2019 is actually not a ban, but would rather correspond to a ‘reduce’ action, as users could still post Infowars links, but these posts generated vastly less engagement. It should be noted that the engagement metrics increased again at the end of 2019 / beginning of 2020, suggesting that the reducing measure may have been lifted a few months after its implementation.

As CrowdTangle is tracking posts only from certain public groups and pages, we also used the ‘/search/articles’ endpoint of the Buzzsumo API, to gather more complete Facebook data. We collected the engagement data for the 14,232 articles crawled by Buzzsumo from the Infowars website between January 1, 2019 and Decembre 31, 2020. The command can be found here.
We observe that the articles published after May 2, 2019 received less Facebook engagement than the ones published before (Figure X5), with a percentage change of -97\% for the reactions, -59\% for the shares and -97\% for the comments. An increase in engagement was also observed in 2020. It reinforces the hypothesis that Facebook reduced the reach of posts sharing Infowars links during a few months in 2019.

We found irregularities in the number of Infowars articles collected from Buzzsumo. While Infowars usually publishes 20-30 articles per day, only 53 articles were collected in the 31-day period between June 11 to July 11, 2020. A temporary crawling problem coming from Buzzsumo may have caused this lack of data. Because no database is perfect, we would like to highlight the importance of cross-checking information between different sources when possible.

@@

%To illustrate we provide two examples linked to the Twitter accounts of the websites $globalresearch.ca$ and $off$-$guardian.org$. Both websites have several failed fact-checks according to \href{https://iffy.news}{iffy.news} - a website which provides a database of websites with low factual reporting levels.\footnote{For $globalresearch.ca$ see \href{https://mediabiasfactcheck.com/global-research/}{https://mediabiasfactcheck.com/global-research/} and for $off-guardian.org$ see \href{https://mediabiasfactcheck.com/offguardian/}{https://mediabiasfactcheck.com/offguardian/}.  }
\begin{figure}
\centering
	\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/globalresearch/sum_globalresearch.ca_6_months.jpg} 
		\includegraphics[scale=0.35]{./img/globalresearch/engagement_sum_rolling_1_globalresearch.ca.jpg}
	\end{multicols}
\caption{}
\label{fig4}
\end{figure}

\begin{figure}
\centering	
	\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/globalresearch/tweet.png} 
		\includegraphics[scale=0.35]{./img/globalresearch/warning.png}
	\end{multicols}
\caption{}
\label{fig4bis}
\end{figure}

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{tto2019}
\usepackage{times}
\usepackage{latexsym}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{lscape}
\usepackage{url}

@@

In this article, we focus on MSMP's policies and actions regarding content with low credibility or false information, commonly referred to as {\it Fake News}.\footnote{For an overview on the {\it concept} of {\it Fake News}, we refer the reader to the article The science of fake news by Lazer et al. (2018)~\cite{lazer}.} The {\it Fake News} phenomenon is still ill-defined by the academic community as it encompasses several combined features such as spreading inaccurate, false or misleading information, with or without the intention of influencing or manipulating a target pool of audience. The growth of social networking platforms over the last decade in terms of number of users worldwide and volume of content, has modified the information ecosystem in terms of production of information and its mediation. Many users can now produce and share content which includes news related information, without having to abide by strict editorial processes that ensure accuracy of information and reliability of sources. In particular, false or inaccurate content produced and shared on social networking platforms concerning the political life or public health may have a potentially harmful impact on the society, in the rare event that it goes viral. This gave rise to a set of heterogenous fact-checking policies across mainstream platforms.\footnote{For an overview of Facebook's third-party fact checking program see see \href{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}. For an overview of Youtube's policy on fact-checking see:  }

@@

%\bigskip

%{\color{red} Policies not specific to misinformation, but to enforce laws + things already used for terrorism and hate speech. Intro or/and Discussion. accounts: hard to say suspension for which.} 
% Misinformation : which law ? not defined !

%public content\\  insights tool \\ owned and operated by \\ Facebook. \\ \href{https://buzzsumo.com}{Buzzsumo}: commercial content \\ database

\begin{table}[]
\centering
\begin{tabular}{|l|c|l|l|l}

\hline
&  \begin{tabular}[c]{@{}l@{}} Application Programming \\ Interface (API)  \end{tabular}                                                                                                                                                                                                                                                                                                                                                                                                                                            &    \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}} Web \\ Scraping \end{tabular}}                                                                                                                                                                 \\ \hline
 \includegraphics[scale=0.05]{./img/fb_logo.png} & \begin{tabular}[c]{@{}l@{}}\href{https://www.crowdtangle.com}{CrowdTangle}  \\ \href{https://buzzsumo.com}{Buzzsumo} \end{tabular}                                                                                                                                                                                                               &      \multicolumn{1}{l|}{}    
\\ \hline
 \includegraphics[scale=0.007]{./img/tw_logo.png}  &  \href{https://developer.twitter.com/en/docs/twitter-api/early-access}{Twitter API V2} & \multicolumn{1}{l|}{\href{https://github.com/medialab/minet/blob/master/docs/cli.md\#twitter-scrape}{Minet tw scrape}}                                                                                                                                                                           \\ \hline
 \includegraphics[scale=0.03]{./img/yt_logo.png}  &  \href{https://developers.google.com/youtube/v3}{Youtube API V3}      &                                                                                                                            \multicolumn{1}{l|}{}                                                                                                                                                                           \\ \hline
\end{tabular}
\caption{Data collection}
\label{tab1}
\end{table}

 %We We are aware that other APIs or databases can be useful on that matter, but we will only mention here the ones about which we have some experience.
%CrowdTangle is a public insights tool owned and operated by Facebook, that exclusively tracks public content from Facebook public groups and pages. BuzzSumo is a commercial content database that tracks the volume of user interactions with internet content on Facebook, Twitter, and other social media platforms. 
%Section 230 in the US + EU 
%Pressure to moderate and mix-up of platforms with public square… 
%Rôle dans la production/médiation : P-M-R 
%Pourquoi faut-il vérifier leurs politiques ? D’une part parce que ce sont les plateformes elles-mêmes qui annoncent leurs effets. D’autre part beaucoup de choses indirectes. 
%Add disclaimer in a footnote early on in the document : document not meant to be an exhaustive overview of all the existing regulations and point to three or four main legal sources for exhaustive references. 
%Such policies include the introduction of notices (Twitter, see link) or flags (Facebook, see…) to signal to users inaccurate or false content, the temporary or permanent suspension of accounts (Twitter) or pages (Facebook), reducing the visibility of posts or pages (Facebook), or blocking users from sharing specific URL links (see link). The objective of this article is twofold. First, we study the impact of a number of  implemented measures by mainstream platforms to tackle (mis)disinformation.

@@

When an account is permanently suspended by Facebook, it disappears from the platform. That is,  the data can no longer be scrapped and it also disappears from the CrowdTangle API.\footnote{CrowdTangle is a public insights tool owned and operated by Facebook, that exclusively tracks public content from Facebook public groups and pages.} Facebook publishes on monthly basis a {\it coordinated inauthentic behavior} report, where it informs how many personal accounts, pages or groups were deleted and to which {\it deceptive network} they may have belonged.\footnote{See the April 2021 report for an example: \href{https://about.fb.com/news/2021/05/april-2021-coordinated-inauthentic-behavior-report/}{https://about.fb.com/news/2021/05/april-2021-coordinated-inauthentic-behavior-report/}} But as long as external persons do not have access to deleted accounts data, these reports cannot be verified by independent researchers or journalists.

@@

\begin{figure}
\centering
	\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/lifesite.jpg} 
	\end{multicols}
	\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/lifesite_rolling_7_lifesite.jpg}
	\end{multicols}
\caption{Panel (a): number of Tweets per day of the Twitter account $@Lifesite$ linked to the website lifesitenews.com from January, 2019 until April 2021. Panel (b): number of Tweets per day that have shared a lifesitenews.com URL link from January, 2019 until April 2021. }
\label{fig2}
\end{figure}

%paragraph strike system + say following example is a manual decision. 
Twitter has implemented a strike system as part of their Civi Integrity Policy\footnote{See \href{https://help.twitter.com/en/rules-and-policies/election-integrity-policy}{help.twitter.com/en/rules-and-policies/election-integrity-policy}} and their COVID19 misleading information policy.\footnote{See \href{https://help.twitter.com/en/rules-and-policies/medical-misinformation-policy}{help.twitter.com/en/rules-and-policies/medical-misinformation-policy} and \href{https://blog.twitter.com/en\_us/topics/company/2021/updates-to-our-work-on-covid-19-vaccine-misinformation}{blog.twitter.com/en\_us/topics/company/2021/updates-to-our-work-on-covid-19-vaccine-misinformation}} Violations of both policies can entail strikes, where two strikes lead to a 12-hour account lock and five or more strikes lead to permanent suspension from the platform. The 12-hour account lock is hard to observe in the data, especially for users who do not have an over the clock tweeting activity. In this section, we provide one example of a temporary suspension\footnote{See the official documentation on the Twitter's Help Center regarding account suspension: \href{https://help.twitter.com/en/managing-your-account/suspended-twitter-accounts}{https://help.twitter.com/en/managing-your-account/suspended-twitter-accounts }.} of a Twitter account, that seems to be the result of a manual decision concerning a Tweet which violated the rules.

The Twitter account of the website lifesitenews.com has been suspended for at least two periods of time: from end of 2019 until fall 2020 for 308 days, then again since January 2021 for having violated Twitter Rules\footnote{See Lifesitenews's article discussing the reason for the suspension: \href{https://www.lifesitenews.com/news/lifesite-is-dumping-twitter-and-so-should-you}{https://www.lifesitenews.com/news/lifesite-is-dumping-twitter-and-so-should-you}. Twitter rules can be found at: \href{https://help.twitter.com/en/rules-and-policies/twitter-rules}{https://help.twitter.com/en/rules-and-policies/twitter-rules}. }. In particular, this website has several failed fact-checks concerning the published articles, according to Iffy.news.\footnote{See \href{https://mediabiasfactcheck.com/life-site-news/}{https://mediabiasfactcheck.com/life-site-news/}}. We collected the activity (tweets, replies, quotes, retweets) on their Twitter account $@LifeSite$ via the Twitter API, using the historical search endpoint.\footnote{See the documentation: \href{https://developer.twitter.com/en/docs/twitter-api/tweets/search/api-reference/get-tweets-search-all}{https://developer.twitter.com/en/docs/twitter-api/tweets/search/api-reference/get-tweets-search-all}.} We then plotted the number of Tweets, Retweets, Quotes and Replies per day, as shown in panel $a$ of figure \ref{fig2}). The two periods of temporary suspension are clearly observed in the data as the user(s) of the account were not allowed to use the functionalities of the Twitter Platform.

@@

In this section, we provide one case study of how Facebook can block a URL as part of its policy enforcement tools. The Beauty of life (\href{https://thebl.com/}{thebl.com/}) is a US-based media company that shares pro-Trump views and conspiracy theories such as QAnon.\footnote{ See \href{https://en.wikipedia.org/wiki/The\_Epoch\_Times\#Removal\_of\_The\_BL\_(The\_Beauty\_of\_Life)\_from\_Facebook}{wikipedia article}.} Facebook has announced on December $20$, $2019$ that ``The BL is now banned from Facebook'' for coordinated inauthentic behavior\footnote{\href{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us/}{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us/}.}, which includes using fake accounts that misrepresent one's identity or using methods to artificially boost the popularity of content. Coordinated inauthentic behavior is a distinct phenomenon from disinformation according to Facebook, as ``most of the content shared by coordinated manipulation campaigns isn’t probably false”.\footnote{See: \href{https://about.fb.com/news/2019/10/inauthentic-behavior-policy-update/}{https://about.fb.com/news/2019/10/inauthentic-behavior-policy-update/}.}

Nevertheless, for the case of the Beauty of Life, both misinformation and coordinated inauthentic behavior are interlinked, according to the fact-checking organization Snopes which had reported about The BL’s activity to Facebook and other various public articles.\footnote{\href{ https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}{ https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}, \href{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}{https://www.snopes.com/news/2019/11/12/bl-fake-profiles/}, \href{https://www.snopes.com/news/2019/12/13/facebook-bl-cib/}{https://www.snopes.com/news/2019/12/13/facebook-bl-cib/}} It took Facebook five months to complete its investigation of The BL before taking action\footnote{See \href{https://www.businessinsider.com/facebook-bans-beauty-of-life-for-inauthentic-behavior-2019-12}{https://www.businessinsider.com/facebook-bans-beauty-of-life-for-inauthentic-behavior-2019-12}.} and Snopes ended its fact-checking partnership with them in February 2020.\footnote{See \href{https://www.snopes.com/2019/02/01/snopes-fb-partnership-ends/}{https://www.snopes.com/2019/02/01/snopes-fb-partnership-ends/}.}

	\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/beautyoflife/fb_bl_1.png}
	\end{multicols}

	\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/beautyoflife/fb_bl_2.png} 
	\end{multicols}

	\caption{Articles from The Beauty of Life website (thebl.com) published between January 1, 2019 and June 15, 2021 and gathered from the Buzzsumo API. (Top) Facebook engagement metrics (average number of reactions, shares and comments per article). (Bottom) Number of articles published per day. The red line marks the date of December 1, 2019. }
	\label{fb_bl}
\end{figure}
%BuzzSumo is a commercial content database that tracks the volume of user interactions with internet content on Facebook, Twitter, and other social media platforms.

To verify Facebook’s ban of The BL domain name, we first tested whether we could post a Facebook message containing a url from thebl.com. This turned out to be impossible. But such manual verification cannot inform us whether the ban applies indeed to all Facebook users and accounts (as we used only our own personal accounts), nor when it has started. To further investigate this policy, we collected data from Buzzsumo.\footnote{BuzzSumo is a commercial content database that tracks the volume of user interactions with internet content on Facebook, Twitter, and other social media platforms.} We used the ``/search/articles'' endpoint of the Buzzsumo API, to collect the engagement metrics $13$ $634$ articles crawled from the $thebl.com$ website between January $1$, $2019$ and June $15$, $2021$.\footnote{The command can be found in the following Github repository: \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect\_facebook\_buzzsumo\_thebl\_data.py}{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect\_facebook\_buzzsumo\_thebl\_data.py}.}

The number of Facebook reactions, shares and comments dropped to zero for TheBL’s articles published after December $1$, $2019$ (see figure \ref{fb_bl} top panel), indicating the start of the ban. We can note that although the ban was communicated in an article published\footnote{See \href{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us}{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us}.} on December $20$, $2019$, it seems to have actually started on December $1$, $2019$. The number of articles published per day was around $50$ until December $20$, $2019$. The this number decreased drastically to reach a {\color{pink} plateau} around $5$ to $10$ articles published per day (see figure \ref{fb_bl} bottom panel). The communication around the ban may have discouraged The Beauty of Life to proceed with their activity. Using Buzzsumo data, a global ban over sharing a thebl.com URL link on Facebook was ascertained. It started on December $1$, $2019$, and was still enforced in June 2021.

@@

@@

	\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/infowars/fb_infowars_1.png}
	\end{multicols}

	\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/infowars/fb_infowars_2.png} 
	\end{multicols}

	\caption{Public Facebook posts sharing an Infowars link in $2019$ and $2020$ collected from the CrowdTangle API. The red line marks the date of May $2$, 2019, when Facebook has announced the ban regarding Infowars. (Top panel) Number of daily posts. (Bottom panel) Engagement metrics: average number of reactions, shares and comments per post. }
	\label{infowars1}
\end{figure}

One of Facebook’s measures to regulate misinformation is to reduce the spread of misleading content through their ranking system. Facebook ranks each post and/or ad by assigning to it a relevancy score, where a high score leads to a high likelihood of the post and/or the ad to appear on a user's newsfeed. Doing so, Facebook can make a post or a whole account less visible by decreasing the relevancy score of its content; this is precisely the $reduce$ measure.\footnote{Lyons, T. (2018, May 22). The three-part recipe for cleaning up your news feed. Facebook Newsroom. \href{https://about.fb.com/news/2018/05/inside-feed-reduce-remove-inform/}{about.fb.com/news/2018/05/inside-feed-reduce-remove-inform/}.} This measure can be verified by looking at the number of views (reach) of a post, but this metric is not available via the CrowdTangle API or on Buzzsumo. Hence we can indirectly investigate the $reduce$ measure by looking at the engagement metrics (likes, comments, shares) related to a given post; which are available via the CrowdTangle API and Buzzsumo. If a post reaches less users because it has a lower ranking, then it is less likely to receive likes, comments and shares, relative to a post with a higher ranking.

%phrase pas accès au reach, mais seulement les engagement metrics
% Owned by Alex Jones, Infowars is usually described as a misinformation website: it is on the Wikimedia global spam blacklist\footnote{See \href{https://meta.wikimedia.org/wiki/Spam\_blacklist}{meta.wikimedia.org/wiki/Spam\_blacklist}.},
%CrowdTangle and Buzzsumo provide access to the interaction metrics on content (engagement), but not to the number of views (or reach), therefore we can only verify the {\it reduce} measure indirectly through a decrease in engagement. If Facebook was reducing the reach of a content via a lower ranking, we would expect the content to be less likely to receive likes, comments and shares, relative to a post with a higher ranking.

To illustrate, we investigate the case of the website $Infowars$. This website appears in the Misinformation Directory of FactCheck.org, among other websites who have posted deceptive content\footnote{See \href{https://www.factcheck.org/2017/07/websites-post-fake-satirical-stories/}{https://www.factcheck.org/2017/07/websites-post-fake-satirical-stories/}.}. Furthermore, the factual reporting of $Infowars$ has been rated {\it very low} by the Media Bias / Fact Check resource of Iffy.news.\footnote{See the Iffy.news page: \href{https://mediabiasfactcheck.com/infowars-alex-jones/}{https://mediabiasfactcheck.com/infowars-alex-jones/}.}

	\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/infowars/fb_infowars_3.png}
	\end{multicols}

	\caption{Facebook engagement metrics (average number of reactions, shares and comments per article) for the Infowars articles published in $2019-2020$ and gathered from the Buzzsumo API. The red line marks the date of May $2$, $2019$, when Facebook has announced the ban regarding Infowars.}
	\label{infowars2}
\end{figure}

On May 2, 2019, Facebook announced they would prohibit users from sharing Infowars content unless, they are explicitly condemning the material.\footnote{See \href{https://www.wired.com/story/facebook-bans-alex-jones-extremists/}{https://www.wired.com/story/facebook-bans-alex-jones-extremists/} and \href{https://about.fb.com/news/2018/08/enforcing-our-community-standards/}{about.fb.com/news/2018/08/enforcing-our-community-standards/}.} To verify the measure, we used the ``/posts/search'' endpoint\footnote{see the documentation for more details: \href{https://github.com/CrowdTangle/API/wiki/Search}{github.com/CrowdTangle/API/wiki/Search}.} of the CrowdTangle API, to collect $37$ $242$ Facebook public posts that had shared a URL link containing ``infowars.com'', published between January $1$, $2019$ and December $31$, $2020$.\footnote{We found in the collected data some Facebook posts that did not directly share an Infowars link (but rather a YouTube or Facebook video containing an Infowars link in its description), thus we excluded such posts from our data to keep only the $27$ $721$ posts directly sharing an Infowars link.} The command used can be found in the following Github repository: \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect_facebook_crowdtangle_infowars_data.sh}{link}. The number of public posts sharing an $Infowars$ link remained globally stable throughout $2019$ (see figure \ref{infowars1} top panel). Thus the measure announced by Facebook doesn't seem to have prevented users from sharing an $Infowars$ link. Nevertheless, a clear drop in engagement was observed on May 2, 2019 (see figure \ref{infowars1} bottom panel). The number of reactions, shares and comments per post have decreased respectively  by $-94\%$,  $-96\%$ and $-93\%$  when comparing the two months before and after May 2, 2019. This suggests the measure taken by Facebook in May $2019$, is not a ban per se, but rather a $reduce$ measure. This is because users could still post $Infowars$ links, but these posts generated less engagement. It should be noted that the engagement metrics increased again by the end of $2019$ / beginning of $2020$, suggesting that the $reduce$ measure may have been lifted a few months after its implementation.

As CrowdTangle is tracking posts only from certain public groups and pages, we also used the ``/search/articles'' endpoint of the Buzzsumo API, to gather a richer Facebook dataset. We collected the engagement data for the $14$ $232$ articles crawled by Buzzsumo from the $Infowars$ website between January $1$, $2019$ and December $31$, $2020$.  \footnote{The command can be found: \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect\_facebook\_buzzsumo\_infowars\_data.py}{here}.} We observe that the articles published after May $2$, $2019$ received less Facebook engagement than the ones published before (see figure \ref{infowars2}), with a percentage change of -$97\%$ for the reactions, -$59\%$ for the shares and -$97\%$ for the comments. An increase in engagement was also observed in $2020$. It reinforces the hypothesis that Facebook reduced the reach of posts sharing Infowars links only during a few months in $2019$.

@@

%To illustrate we provide two examples linked to the Twitter accounts of the websites $globalresearch.ca$ and $off$-$guardian.org$. Both websites have several failed fact-checks according to \href{https://iffy.news}{iffy.news} - a website which provides a database of websites with low factual reporting levels.\footnote{For $globalresearch.ca$ see \href{https://mediabiasfactcheck.com/global-research/}{https://mediabiasfactcheck.com/global-research/} and for $off-guardian.org$ see \href{https://mediabiasfactcheck.com/offguardian/}{https://mediabiasfactcheck.com/offguardian/}.  }
